\newpage
\subsection{Gavin}
\subsubsection{Summary}
This project was quite a special experience in the sense that we faced many unexpected problems, as well as learning a lot of things.\\

My role varied and I did different parts. I have made the foundation of the functionalities of Defender module, as well as building the whole ammo strategy. Later I participated in refactoring the code, mainly doing refactor on modules that I have participated in building. Lastly, I have written multiple chapters of the report, such as preface, summary, conclusions, bugs and testing, recommendations and more. 
During the course of the project, due to various different problem surfaced, our role changed dynamically to tackle these issues. I feel that the planning in roles could have been better and we could have achieved much more with planning and better tickets.\\

There were problems during the project, varying from bugs in the program to problems in the language itself during the project. It was quite the experience since all projects before used existing languages and software that were robust. Goal, however, caused multiple issues, breaking our code. I also had issues with git, since there was a lot of merge conflicts and often I had to backup and reset. Given that though, proceeding to work in an environment that was still beta was the most challenging.\\

The project was an extraordinary and valuable experience. I have learned a lot and I believe that we could achieve much better result next time if we were to do a similar project.
\subsubsection{Reflection}
I participated in this project as a member. My role varied quite a lot during the course of this project. There were quite some problems that I faced which I will discuss below.

\noindent
\paragraph{Contributions}
\begin{itemize}
\item[-] \textbf{Defender.}
My part of work initially included the making of the defender bot. I created the first few versions of the defender and its basic functionalities such as picking first weapon and standing on the flag. Later the job was passed on to Youp, who continued and improved the defender.
\item[-] \textbf{Ammo Strategy.}
After the defender, I made the ammo strategy for the Roamers, and then participated in the refactoring. The ammo module was a result of this, which included a list of weapon ammo to compare and decide if the bot needs to pick up ammo.
\item[-] \textbf{Overlord.}
There were also attempts to create extra functionalities for the overlord. The extra functions included possible role switching during the game, as well as a system where the flag carrier would call out for escort if it is carrying the flag. The functions where eventually scrapped after the decision that the existing code has to be fixed first.
\item[-] \textbf{Report.}
In the last few weeks I devoted my time to making the report, making the Preface, Summary, Conclusion, Bugs and Testing part and checked the report for grammar. After the meeting with the professor of the course technical writing, I rewrote most of the report in subjective tone to address the issue that our report was using objective tone in most parts.
\end{itemize}
\noindent
\paragraph{Problems}
\begin{itemize}
\item[-] \textbf{Git}
A big problem for me was git, git itself required quite sometime to learn, and merge conflicts were even a bigger problem, there were countless occasions where I had to backup stuff and invoke a hard reset to solve the problems. Whenever I wasn't fast enough with pushing commits, merge conflicts would happen and git often failed at merging. Most of the time I had to backup and hard reset it.
\item[-] \textbf{GOAL plugin}
Another thing that often caused problems for me was the GOAL plugin. The plugin had many bugs which often led to false alarms, crashes. GOAL plugin doesn't recognize modules, and has warnings all over code that ran normally. Moreover, it doesn't recognize the code in modules, representing those in text form, which defeats the purpose of using a IDE on some level.
\item[-] \textbf{Time management and planning}
Another issue during the project was the planning. Especially in the begin of the project, we didn't really understand the use of Trac. As a result, the planned tickets were sometimes to vague, description wasn't enough, and at times the product of the ticket wasn't really what the other group mates expected.
\end{itemize}
\paragraph{Improvements}
I believe that the main improvement we could do is in the planning part. As in the course of the project, many problems rose and we often had to improvise. One of this example would be the messy code not working and we had to refactor the code. This occupied a lot of valuable time and caused some shift in the various roles of everyone. Also at times the steps and short term goals were not quite clear, resulting in us blindly working towards somewhere that we hope the code would improve the performance while we should have a much clearer goal so that we could work efficiently, as well as potentially motivate the team and raising morale. I believe that we can achieve a much better result, if we were to do similar projects in the future