\newpage
\subsection{Jelle}
\subsubsection{Summary}

\subsubsection{Reflection}
This was quite an interesting project, in ways beyond the subject matter. My role in this group started primarily in helping with the design of the program which later shifted more in programming as the situation demanded.

At the start of the project when the favored design of the program was still unclear I tried to come up with possible structures and strategies. I believe that this contributed to the project although sometimes I would get to overzealous. This would causes my ideas to become impractical. 
Later when the general outline of the program became clearer my role naturally transferred to a more practical role as programmer. My primarily flaw in this role is that I have the habit to work to close to deadlines. This does not always have an direct adverse effect on the results but it is never a desirable trait. 

The work that I contributed to this project was primarily programming. Half way the project we found that the initial structure of the project limited us in the possibilities of our code. We wanted to be able to implement a ‘dynamic role assignment’ which was practically impossible with our current code. The solution to this problem would be refactoring of the whole program in a more module based form. I worked on this together with Joshua but this still took a full week. 
I also programmed a couple of modules and of course helped with some fixing of the program. 

I actively participated to the project, especially when the subject entailed design. This of course could also backlash because I sometimes thought that I pressed other people out of the discussion. However I believe that my voice was also beneficial in that it caused some discussion in the group.
I believe that I learned quite a lot during this project. In the future I will try to keep my ideas a bit more sane and give other people room to talk. But the primary lesson is to avoid deadlines. It is better for everybody if work is done far in advance so that any nasty surprises can be dealt with easily instead of late at night 
