\chapter{Progress report}
%\addcontentsline{toc}{chapter}{Appendix B: Progress report}

In this appendix our group coordination contract can be found, just like a discussion and reflection on our group coordination and management.

\section*{Group cooperation contract}

To make sure that we are all on the same page and that we will work together well, we have designed a group coordination contract.
\subsubsection{Task allocation}
The project roles and matching tasks that we have are as following:
\begin{itemize}
\item[-] \textbf{The Chair of Meeting} will lead meetings and prepare agendas for them.
\item[-] The \textbf{Secretary} will take minutes during the meetings.
\item[-] The \textbf{Trac Wiki Manager} will make sure that the Trac wiki stas up to date.
\item[-] The \textbf{Task Coordinator} will make sure that everyone does what they are supposed to do.
\item[-] The \textbf{Planners} will make sure that the group stays on schedule.
\end{itemize}

We divided the roles between the group members and came to this division of tasks:

\begin{description}[noitemsep]
\item[Lisette] Chair of Meeting
\item[Ashay] Secretary
\item[Joshua] Trac Wiki Manager
\item[Jelle] Task Coordinator
\item[Gavin] Planner
\item[Youp] Planner
\end{description}

\subsubsection{Decision Making}
Our goal is to look at the capabilities of the team members, and with that in mind, we'll assign tasks. If someone encounters a problem, he/she should immediately inform the other team members through WhatsApp. (i.e. problems with git, coding problems). If no-one of the team can fix the problem, he/she should contact the TA. Design choices will be discussed during meetings. If the decision is not unanimous, the majority rules. When a vote is tied, both sides of the argument will be explained and discussed further. If nobody is willing to change their vote, the Chair of Meeting will break the tie.

\subsubsection{Presence and Availability}
If a team member will be absent during a meeting, he/she should tell the others at least one week before the meeting. If he/she has a good reason for the absence, the one week before rule doesn't count. He/she should finish his/her tasks even when he/she is absent. When someone is absent, without telling, or doesn't have a good reason and/or didn't finish his/her tasks, this will be reported to the TA, he/she should bring a treat. Before reporting, a team member will notify the person in question via WhatsApp.
\subsubsection{Meetings and Schedules}
The Chair of Meeting prepares the agenda for every meeting.
The agenda should be final and shared with the group at 00:00 on Tuesday at the latest, so the group can prepare for the meeting and suggest edits when needed.
We'll have meetings with the TA on every Tuesday, and if necessary, we'll plan another meeting. If a team member encounters an issue which concerns the whole group, he/she should contact the Chair of Meeting and then it can be put on the agenda for the next meeting.

\section{Evaluation of the cooperation during the project}
We had no problems with the most important part of cooperation. Everyone was willing to do their part and to make the project a success, and there were no fights or unprofessional arguments. We got along great and all arguments were concerning content, not concerning persons or their work ethics. The working atmosphere was pleasant, which of course had a huge influence on the actual work. The absence of free-riding for example, severely boosted the motivation of all team members, as laziness would result in a guilty conscience, while working did not feel like doing someone else's work. Another good example is that the big stick, the cooperation contract, was not used once, implying the work was done in mutual harmony.

Other parts of the cooperation were not huge issues either, but some improvements could be made. This was true for communication, which could be used in a more effective manner, as well as for planning. Both of these could be applied in a more structured manner, resulting in a more effective form of collaboration. In future projects for example, it could be a good idea to split certain tasks into multiple smaller tasks beforehand. This would allow the team to monitor the progress in a better way, allowing interference earlier on, while at the same time allowing the person executing the task to keep track of the situation better, allowing him or her to ask for assistance in a timely matter.

\section{Use of Trac}
Trac came in quite handy once we started the project. Creating tickets on Trac forced us to think about the tasks we were going to focus on in the next sprint. This helped us to have structure in our work and to have an overhead about all the things that should happen before the upcoming deadlines. Overall, Trac was great for helping us manage our project. Despite this, Trac was used less towards the end of the project, as it was often quicker to resolve an issue directly. Still, this caused us to lose track of certain issues, so in future projects Trac should be used more consistently.

During this project, we gradually started understanding Trac more and more (for example the milestones and how we could adjust them), so we're quite proficient in Trac now, making it even more useful in future projects.

\input{contents/appendix/progress/reflection/reflection}

\section{Project evaluation}
Overall, we found the project very interesting. The use of (computer) games is always a good way to make education more interesting and usually it helps with understanding and digesting the material, but it's in our opinion especially well-tailored for the domain of artificial intelligence. Despite this, there is definitely still room for improvement.\\

\subsection{The use of Goal}
Our biggest point would be the use of Goal. As a group, we feel that it is still to early to build the entire project around a tool that is essentially still in the development cycle. We have encountered various issues regarding Goal, ranging from minor inconveniences to critical. The program refuses to run on most virtual machines, due to problems with file-paths, and was unavailable due to a corrupted update for over a week. We have also encountered unspecified or buggy behaviour on multiple occasions, just as performance issues. Besides this, semantic errors in Eclipse are often plain wrong and debugging is a real nuisance. However, taken into account the stories that have reached us regarding last year's project, we are confident that most of these issues can be fixed by next year.

Another improvement that could be made is the number of available primitives, as they are currently quite limited. This meant unorthodox, creative or advanced solutions required complex workarounds or were practically impossible to implement (look away from the flag, hide in a corner, cover behind a wall, zigzag when shot at etc.). The already available primitives were practical and easy to use though.

\subsection{Compulsory practicals}
The compulsory practicals were in our opinion unnecessary, if not counterproductive. A university is a place where, apart from applicable knowledge, other values should be taught, such as responsibility. Compulsory education and forced attendance have no place in this.

Apart from this, practicals were often inconvenient and incompatible with other obligations, such as work or extracurricular activities (especially on Friday till 17:30), and the location was often noisy, resulting in a loss of concentration. Having regular meetings could be made obligatory, but having to work for four hours at a specified time did not add anything. 





