\addcontentsline{toc}{chapter}{Summary}
\chapter*{Summary}
In order to show our understanding of and proficiency in multi-agent systems and logic based AI, our target is to create a multi-agent system to compete with other bots in the game/environment Unreal Tournament 3. Our objective is to win in Capture the Flag games against a team of the environment's native bots of various levels and in differing amounts.
 
As the native bots are quite strong in the game, creating a multi-agent system that can lead our team of bots to victory is not easy. There are several objectives to be achieved in order to win against the bots of the highest level, such as strategy, code efficiency, as well as avoiding bugs and overcoming technical difficulties.

Firstly, from a design perspective, several strategies for the enhancement of cooperation among bots were designed. These designs included a macro strategy for the team, controlling positioning, role assignment and combat tactics, as well as micro strategies for the various simpler tasks, such as collecting (preferred) weapons and other items.

Secondly, from a technical perspective, victory can only be achieved with efficient code. This has a huge influence as the efficiency directly correlates to the number of cycles that can be processed per second, putting constraints on the reaction speed of individual bots. This meant coding problems had to be solved and refactoring was essential to properly structure the code and remove bottlenecks. The use of modules instead of classes made sure repeated code was minimal and the bots could run with high efficiency. 

Thirdly, in the process of creating the features mentioned above various bugs and technical problems occurred, ranging from nearly harmless to catastrophic. Each of them had to be solved, be it by developing a solution or by creating a workaround. Some of the issues were game-breaking, stalling the project and had to be fixed immediately, while others were minor annoyances creating unwanted bot behaviour.

All these as well as the above mentioned design strategies, features, and problems are recorded in detail in the report.