\chapter{Analysis of the UT environment}

The ten scenarios are:
\begin{enumerate}
	\item The first scenario is when the Flag capturer captures the enemy flag. His goal is to grab the enemy flag, and when he percepts that he is holding the flag, his goal is to bring it back to his base. If he does not encounter an enemy, he heads straight to the base. When he does encounter an enemy, his priority is killing the enemy. If he succeeds, he continues delivering the flag. Eventually he will be defended by the roamers and Defender, so he can easily run back to his base.\\
	\item The second scenario is when the Flag Defender encounters an enemy. At first, he roams around his own base. If he is stuck, he automatically respawns. When he sees an enemy, his priority is to kill him. When the Defender is hit, he will go grab health. If he is killed by the enemy, the Defender respawns and will roam around his base again. When he sees the same enemy as before, he will again try to kill him. But if he can not see the enemy anymore, he will not try to pursue him, bot stay around the base. We chose this, because we did not want that the Defender would leave his position, otherwise we would be very vulnerable. The enemy who got away, should then be taken care by the roamers and perhaps the Flag Capturer.\\
	\item The third scenario is when the roamers see an enemy. If they see an enemy, their priority is to kill them. They will pursue the enemy trying to kill them. When the flag capturer has grabbed the enemy flag and runs back to his base, and he is pursued by an enemy, the roamers automatically set their goals to kill them. The fact that the enemy is pursuing the Capturer, is not important. This is what makes the roamers so lethal. \\
	\item The fourth scenario is when one of the roamers is hit. When the enemy hits one of the roamers, and their health is dropped below 100, he will adopt a new goal to leave the battlefield and grab some health. This will only happen if he sees a health pack. When his health is 100 again, he goes back to defeat the enemy if he sees one. There is also a big health, which boosts it to 180. If the roamer sees one, he will adopt the goal to grab it.\\
	\item The fifth scenario is when the roamers are low on ammo, or when they see a new weapon, or armor. If they percept that they are low on ammo, the new goal is to grab the ammo. When they have grabbed it, they will continue with what they were doing. If the bot sees a weapon, he will first check if he already has the weapon. If he does not have, his goal will be to pick the weapon up. This also counts for armor, he will first check if he already has this specific armor, if not, he will try to grab it. \\
	\item The sixth scenario is when the roamers end up capturing the flag. If the roamers does not have any goals, he would be inactive. Instead of being inactive we decided that when he reaches this point, he should go to the enemy base and try to grab the flag. Once he captures the flag, he basically becomes a Flag Capturer, and he will try to deliver it back to his own base. If he encounters an enemy while holding the flag, he will try to defeat him, and when that happens, he will continue delivering the flag.\\ 
	\item The seventh scenario is when the Flag Capturer sees a weapon. He percepts that there is a weapon, then he looks at his beliefs and checks if he does not own that weapon already. If he owns it, he will continue trying to capture the enemy flag. If he does not owns it, he will adopt the goal to pickup the weapon. After the pickup he will continue trying to capture the enemy flag.
\end{enumerate}